Joint analysis of read count data

### 2020-09-11 combined_analysis/combine_all_DLPFC.Rmd
Inital commit

### Create residuals
```{r Create residuals}

form = ~ Dx*Reported_Gender + RIN + ageOfDeath + scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate)

@@

### Test marginals
```{r differential.expression.simple}

@@

```{r plot.meta.analysis.SCZ, fig.height=5, fig.width=10}
# volcano plot for meta-analysis
main = paste('Meta-analysis', coef, sep = ': ' )
plotVolcano( df_meta_SCZ, df_meta_SCZ$Symbol[1:20] ) + ggtitle( main )
```

>>>>

```{r Create.residuals}

### Create residuals
form = ~ Dx*Reported_Gender + RIN + ageOfDeath + scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate)

@@

```{r check.correlation}
ngenes = 2000
C1 = cor(t(residuals.lst[[1]][1:ngenes,]))
C2 = cor(t(residuals.lst[[2]][1:ngenes,]))

df = data.table(A   = as.numeric(C1[lower.tri(C1)]),
                B   = as.numeric(C2[lower.tri(C2)]))

df$density <- get_density(df$A, df$B, n = 100)
ggplot(df, aes(A, B, color=density)) + geom_point() + geom_point(size=.4) + theme_bw(15) + theme(aspect.ratio=1, legend.position="bottom", plot.title = element_text(hjust = 0.5)) + geom_abline(color="red") + scale_color_viridis() + xlim(-1,1) + ylim(-1,1) + xlab(paste0('Correlation (', names(residuals.lst)[1], ')')) + ylab(paste0('Correlation (', names(residuals.lst)[2], ')'))
```

### Test marginals for Schizophrneia vs controls
```{r differential.expression.simple}

@@

```{r plot.meta.analysis.SCZ, fig.height=5, fig.width=10}
# volcano plot for meta-analysis
main = paste('Meta-analysis', coef, sep = ': ' )
plotVolcano( df_meta_SCZ, df_meta_SCZ$Symbol[1:20] ) + ggtitle( main )

pi1 = 1 - qvalue(df_meta_SCZ$P)$pi0
data.frame(pi1) %>% kable(caption="pi1 for SCZ meta-analysis") %>% kable_styling(full_width=FALSE)

```

# Test RCSD anbd ADAMTS2
